### 2019-07-31 introduction.tex
Figures W18 added, more writting in Intro TTV

\begin{figure}[H]
\centering
\includegraphics[width=0.8\columnwidth]{imagenes/exo_dischist_cumulative.png}
\caption{Accumulative number of discovered exoplanets by year.}
\label{amount_exoplanet}
\end{figure}

@@

The Transit Timing Variations technique was proposed as a way to detect Earth-mass planet in multiplanetary systems due to gravitational interactions \citep{Holman2005,Agol2005}. A planet in a Keplerian orbit will transit its star following a linear function of the orbital period (Eq.~\ref{linear_ephemeris}), but the presence of a second planet could produce transits no exactly periodic, thus the time between two consecutive transits varies.

@@

In Equation .~\ref{linear_ephemeris}, $P$ is the orbital period and $E$ is an arbitrary epoch with the corresponding transit time $T_{c}(E)$. For a given light curve (see Figure \ref{transit}), the transit time is computed as:

The variation in time produced by the perturbing body depends on the mass and geometry of their orbits. The magnitude of the variation between successive  transit is:

\begin{equation}
\Delta t = \frac{45\pi}{16} \frac{M_2}{M_*} P_{1} \alpha^3_{e} (1-	\sqrt{2}\alpha^{3/2})^{-2}
\end{equation}

Where $\alpha_e = \frac{a_1}{a_2(1-e_2)}$, $a_1$ and $P_1$ are the semi-major axis and orbital period of the transiting exoplanet, while the perturbing planet has a mass $M_2$, semi-major axis $a_2$  and orbital period $P_2$

@@

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{imagenes/exo_dischist_cumulative.png}
\caption{Accumulative number of discovered exoplanets by year.}
\label{amount_exoplanet}
\end{figure}

@@

The Transit Timing Variations (TTV) technique was first proposed as a way to detect Earth-mass planets in multiplanetary systems due to gravitational interactions with a transiting exoplanet \citep{Holman2005,Agol2005}. However, TTVs can be also use to measure tidal interactions between the planet and the star or to detect exomoons \citep{Kipping2009a,Kipping2009b}, among others.

For a given light curve of a transiting exoplanet (see Fig. \ref{transit}), the transit time $T_{c}$ (or central time of the transit) is computed as:

A single transiting planet will stay in a Keplerian orbit around its host star, producing a transit time strictly periodic. Thus, the transit time $T_c$ follows a linear function of the orbital period $P$:

@@

Where $T_0$ is a reference transit time and $E$ is the number of epochs since $T_0$.  The presence of a second planet produces transits no exactly periodic, hence Eq.~\ref{linear_ephemeris} will not be valid. As the transit times will be no longer a linear function,  the time between  transits varies.  The variation in time produced by the perturbing body depends on the mass and geometry of their orbits. The magnitude of this variation between successive transits of the transiting planet is:

\begin{equation}
\Delta t = \frac{45\pi}{16} \frac{M_2}{M_*} P_{1} \alpha^3_{e} (1-	\sqrt{2}\alpha^{3/2})^{-2}
\label{delta_t}
\end{equation}

Where $\alpha_e = a_1/(a_2(1-e_2))$ is the ratio of the semi-major axis of the planets, considering a nonzero eccentricity for the perturbing planet ($e_2 \neq 0$) and $a_1 < a_2$. The semi-major axis of the transiting exoplanet is $a_1$ and its orbital period $P_1$, while the perturbing planet has a mass $M_2$, semi-major axis $a_2$, orbital period $P_2$ and eccentricity $e_2$. Assuming that the orbital parameters of the known transiting exoplanet are already derived from its light curve, the orbital parameters and mass of the hypothetical pertuber can be estimate numerically \citep{Nesvorny2008,Nesvorny2009}, even if the second planet does not transit the star.

The TTV method is a efficient tool to search for additional unseen companions, since in order to employ this technique only photometry of the transiting exoplanet during a transit events is required. Moreover, this technique enhances its sensitivity when the two bodies in the system are close to Mean Motion Resonances (MMR) \citep{Agol2005,Steffen2005,Agol2007} (see Figure~\ref{rms_ttv_amplitude}) .

\begin{figure}
\centering
\includegraphics[width=0.6\columnwidth]{imagenes/rms_ttv_amplitude}
\caption{Example of a system with a transiting exoplanet of $1~M_{J}$ in a 10-day orbit, around a star with $0.367~M_{\odot}$. The perturber is a Earth-mass planet. Panel \textbf{a} is an O-C diagram showing the measured TTV when the pertuber has a period of 16.11 days, not in Mean Motion Resonance with the transiting planet. Panel \textbf{b} shows the TTV when the transiting planet and the perturbing planet are near an interior 2:1 resonance. The amplification of the TTV signal is by an order of magnitude. (Figure from \cite{Haghighipour2011})}
\label{rms_ttv_amplitude}
\end{figure}

\cite{Holman2010} presented the first multiplanetary system confirmed using the TTV method: Kepler-9b and Kepler-9c.

The no detection of TTV is also important: architecture of the system.

@@

This thesis is an extension of the Transit Monitoring in the South project (TraMoS, see Chapter\ref{chap:tramos}) started in 2008 by Sergio Hoyer and Patricio Rojo. I selected a new sample of transiting exoplanets, all of them hot Jupiters without any companions detected to date.
